%-------------------------
% Resume in Latex
% Author : Andrei Shestakov
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{. #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://ornicum.ru/}{\Large Andrei Shestakov}} \\
  DOB: July 10 1984 & Email : \href{mailto:ornicum@gmail.com}{ornicum@gmail.com}\\
  \href{http://ornicum.ru/}{http://ornicum.ru} & Mobile (Russian Federation) : +7-961-610-9035 \\
  Skype id : ornicum & Mobile (Belarus) : +375-29-314-59-08 \\
\end{tabular*}

  I have also Telegram, WhatsApp and Viber on russian mobile phone. It will be better to connect via Internet.


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Novosibirsk State Technical University}{Novosibirsk, Russia}
      {Bachelor of Applied Mathematics and Computer Science (Statistics); GPA: 4.32 / 5.00 } {Sep. 2002 -- June. 2007}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SK Hynix Memory Solutions Eastern Europe}{Minsk, Belarus}
      {Senior Software Engineer}{May 2018 - Present}
      \resumeItemListStart
	\resumeItem{Description}
	 {SK Hynix R\&D center in Minsk specialized in SSD development. There are several departments: SSD HardWare Verification, Advanced Algorithms, FirmWare, Tools, HardWare Simulator and Software Quality Engineering.

	SK Hynix has several SSD projects per year. It can be SATA or NVMe projects also the projects at the same time can be Client or Enterprise. Enterprise SSD has some capacitors that help to save cached data to NAND in 15 microseconds.}
	\resumeItem{Role}
	{I'm working in SQE team and lead project for testing Vendor Specific Commands (it's command set for different Vendor Specific Tools for SSD). My main task is not writing tests for Vendor Specific Commands only, but also creating arcitecture and infrastructure for making all Vendor Specific Command tests common, if it's possible.}
        \resumeItem{Technologies}
          {Python 2.7 and internal framework, C and C++ code debug.}
      \resumeItemListEnd


    \resumeSubheading
      {Freelance}{Russia}
      {Software Engineer}{2009 - Present}
      \resumeItemListStart
        \resumeItem{Description}
          {There were many different projects.

           There are biggest and most interesting.
          
          1. System for scraping, collecting and analysing data from bookmaker's sites. It was written on Django.
          
          2. System for collection data from sport exchange betfair.com and also tools for statistical analysis. It was system with complex architecture that using server software written on C++, PostgreSQL as database, Redis for collecting bad structured data, Tornado as web-part server, web-sockets.

          3. Web currency exchanger. Also in this project I wrote begin part of internet banking.}
        \resumeItem{Role}
          {System Administrator, C++ Software Engineer, Python Software Engineer.}
      \resumeItemListEnd

    \resumeSubheading
      {Mobalytics}{Saint Petersburg, Russia}
      {Senior Software Engineer}{Oct 2016 - Sep 2017}
      \resumeItemListStart
        \resumeItem{Description}
          {It's a startup for competiteve e-sports gamers like online coucher. There were several projects: know-how as GPI (General Performance Index), pre-game, post-game and statistics.}
	\resumeItem{Role}
	  {I led project named "Statistics" that shows different statistic characteristics of player for matches, seasons, characters and so on.}
        \resumeItem{Technogies}
	  {We changed technologies stack 5 times per year. Started from Python 2.7, Django, Postgresql, Celery, RabbitMQ and ended on Python 3.6, Cassandra, asyncio, Microservices, Kubernetes}
      \resumeItemListEnd

     \resumeSubheading
      {EMA ltd}{Novosibirsk, Russia}
      {Software Engineer} {Jul 2007 - Aug 2008}
      \resumeItemListStart
        \resumeItem{Description}
          {Automation in Energetics. Company had 14 server and several client solutions for different tasks on power plants.}
        \resumeItem{Role}
          {My main tasks.
            \begin{itemize}
	   \item Migration system calls library from OS iRMX to Linux.
              \item Developing and support server software.
              \item Developing architecture of separate parts of software.
              \item Writing documentation.
            \end{itemize}
          }
        \resumeItem{Technologies}
          {C, Oracle}
      \resumeItemListEnd

    \resumeSubheading
      {Lucena Research}{Atlanta, GA}
      {Data Scientist}{Summer 2012 and 2013}
      \resumeItemListStart
        \resumeItem{Portfolio Management}
          {Created models for portfolio hedging,  portfolio optimization and price forecasting. Also creating a strategy backtesting engine used for simulating and backtesting strategies.}
        \resumeItem{QuantDesk}
          {Python backend for a web application used by hedge fund managers for portfolio management.}
      \resumeItemListEnd

    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, CA}
      {Research and Teaching Assistant}{Jan 2012 - Dec 2013}
      \resumeItemListStart
        \resumeItem{Research Assistant - Machine Learning}
          {Research on machine learning for portfolio hedging and replication algorithms. Modeling low-risk \& continuous-return strategies. Developed the python library QSTK.}
        \resumeItem{Teaching Assistant - Computational Investing}
          {The online course on Coursera, had more than 100,000 students enrolled. It was featured on the 11 Alive News and the Atlanta Journal Constitution. Involved in creating assignment, exams and conducting recitation sessions. Also taught the on-campus version of the course.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{QuantSoftware Toolkit}
      {Open source python library for financial data analysis and machine learning for finance.}
    \resumeSubItem{Github Visualization}
      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
    \resumeSubItem{Recommendation System}
      {Music and Movie recommender systems using collaborative filtering on public datasets.}
    \resumeSubItem{Mac Setup}
      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

